The promise of community-driven preprints in ecology and evolution

### 2024-10-21 ms/ms.qmd
Updated panel D academic age and gender to only be about preprints not articles (postprints removed)

##-------------------##
# Career Stage (everything)
##-------------------##
#compute academic age! (Zoe X)
 age <- data2 %>% 
  mutate(preprint_published_year_z = year(preprint_published_date)) %>% 
  mutate(academic_age = (preprint_published_year_z-submitting_author_first_publication_year))

@@

  data4 <- left_join(data3, data3_update, by = c("submitting_author_ASCII", "submitting_author", "submitting_author_country", "preprint_title"))
  #table(data4$gender.x, useNA = "always")
  #table(data4$gender.y, useNA = "always")
  data4$gender.x[is.na(data4$gender.x)] <- data4$gender.y[is.na(data4$gender.x)] #replace with correct values
  data4 <- rename(data4, gender = gender.x)
  #table(data4$gender, useNA = "always") #more males than females, two NA ue to missing first name / collective authorship

  # Plot the data
  ###Zoe's gender pie###
  #female - 37.8, male - 62.2

  gender <- c("female", "male")
  percentage <- c(37.8, 62.2)
  sex_ratio<- data.frame(gender, percentage)

  sex_ratio <- sex_ratio %>% ggplot(aes(x = "", y = percentage, fill = gender)) +
      geom_col(color = "black")+
    scale_fill_manual(values = c("white", "black")) +
      coord_polar(theta = "y") + 
      theme_void()

  ggsave(here("output", "figs", "sex_ratio.svg"), sex_ratio)

  ##Pie was then imported to illustrator for aesthetic touches and to combine with other plots in Figure 1. - Zoe X

  # Load in and plot the final figure
    fig <- image_read(here("output", "figs", "Figure 1_FINAL.png")) 
    fig

@@

Research can take a while to be published (see below). Early and Mid-Career Researchers (EMCRs) (~10 years post-PhD) are under pressure to publish rapidly to be competitive in job applications, promotions, and obtaining grants to progress their careers [@vale2015accelerating; @sarabipour2019value]. Preprints are especially useful for EMCRs because they can achieve faster dissemination and greater visibility [@fu2019releasing]. EMCRs may therefore be expected to make use of preprints more than colleagues at later career stages because they are more often in charge of article submission and have developed their careers in an environment where preprints are a normal part of the publication process. We collected data on the 'academic age' of submitting authors by looking at Google Scholar profiles of authors (when available) and recording their first year of publication in a peer-reviewed journal. While this is a rough estimate of career stage, there was evidence that the number of preprints posted decreases with later career stages (negative binomial glm: year slope = `r res[2, "Estimate"]`, SE: `r round(res[2, "Std. Error"], 2)`, *p* < 0.001, n = `r nrow(count_dat[complete.cases(count_dat),])` years). Most preprints were submitted by authors who published their first paper in the last ~10 years ([@fig-summary]E), with the median year since first publication being `r median(data2$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r mean(data2$submitting_author_first_publication_year, na.rm = TRUE)`; SD = `r sd(data2$submitting_author_first_publication_year, na.rm = TRUE)`, n = `r sum(complete.cases(data2$submitting_author_first_publication_year))`). These patterns support the expectation that EMCRs may use preprints to make their work more visible and disseminate their findings more quickly. However, we acknowledge that understanding the reasons why EMCRs might adopt preprint servers more does require community surveys as has been done in other studies [e.g., @fraser2022motivations].

>>>>

##-------------------##
# Career Stage (everything)
##-------------------##
#compute academic age! (Zoe X)
 age <- preprints %>% 
  mutate(preprint_published_year_z = year(preprint_published_date)) %>% 
  mutate(academic_age = (preprint_published_year_z-submitting_author_first_publication_year))

@@

  data4 <- left_join(data3, data3_update, by = c("submitting_author_ASCII", "submitting_author", "submitting_author_country", "preprint_title"))
  #table(data4$gender.x, useNA = "always")
  #table(data4$gender.y, useNA = "always")
  data4$gender.x[is.na(data4$gender.x)] <- data4$gender.y[is.na(data4$gender.x)] #replace with correct values
  data4 <- rename(data4, gender = gender.x)

  # Now, isolate just preprints because this question is focused on preprints.This object is used for the pie chart.
  data4_preprints <- data4  %>% filter(time_between_preprint_and_pub_days >= 60 | is.na(time_between_preprint_and_pub_days))

  #more males than females, two NA ue to missing first name / collective authorship
  gender_table <- data4_preprints  %>% tabyl(gender)  %>% filter(!is.na(gender))

  # Plot the data
  ###Zoe's gender pie###

  sex_ratio <- gender_table %>% ggplot(aes(x = "", y = percent, fill = gender)) +
      geom_col(color = "black")+
    scale_fill_manual(values = c("white", "black")) +
      coord_polar(theta = "y") + 
      theme_void()

   ##Pie was then imported to illustrator for aesthetic touches and to combine with other plots in Figure 1. - Zoe X
  ggsave(here("output", "figs", "sex_ratio.svg"), sex_ratio)

  # Load in and plot the final figure
    fig <- image_read(here("output", "figs", "Figure 1_Revised.png")) 
    fig

@@

Research can take a while to be published (see below). Early and Mid-Career Researchers (EMCRs) (~10 years post-PhD) are under pressure to publish rapidly to be competitive in job applications, promotions, and obtaining grants to progress their careers [@vale2015accelerating; @sarabipour2019value]. Preprints are especially useful for EMCRs because they can achieve faster dissemination and greater visibility [@fu2019releasing]. EMCRs may therefore be expected to make use of preprints more than colleagues at later career stages because they are more often in charge of article submission and have developed their careers in an environment where preprints are a normal part of the publication process. We collected data on the 'academic age' of submitting authors by looking at Google Scholar profiles of authors (when available) and recording their first year of publication in a peer-reviewed journal. While this is a rough estimate of career stage, there was evidence that the number of preprints posted decreases with later career stages (negative binomial glm: year slope = `r res[2, "Estimate"]`, SE: `r round(res[2, "Std. Error"], 2)`, *p* < 0.001, n = `r nrow(count_dat[complete.cases(count_dat),])` years). Most preprints were submitted by authors who published their first paper in the last ~10 years ([@fig-summary]E), with the median year since first publication being `r median(prepints$submitting_author_first_publication_year, na.rm = TRUE)` (mean = `r mean(prepints$submitting_author_first_publication_year, na.rm = TRUE)`; SD = `r sd(prepints$submitting_author_first_publication_year, na.rm = TRUE)`, n = `r sum(complete.cases(prepints$submitting_author_first_publication_year))`). These patterns support the expectation that EMCRs may use preprints to make their work more visible and disseminate their findings more quickly. However, we acknowledge that understanding the reasons why EMCRs might adopt preprint servers more does require community surveys as has been done in other studies [e.g., @fraser2022motivations].
